### 2022-06-02 LaTeX/report.tex
Updates

\isabelle{
    {\color{isa_blue}{function}} dfs :: "\generic{v} $\Rightarrow$ \generic{v} env $\Rightarrow$ \generic{v} env" \and{}\\
    $~~~~~~~~~~$dfss:: "\generic{v} $\Rightarrow$ \generic{v} set $\Rightarrow$ \generic{v} env $\Rightarrow$ \generic{v} env" \where\\
    "{\color{isa_dark_blue}dfs} {\color{isa_dark_green}v e} =\\
    $~~~~~$({\color{isa_blue}{let}} {\color{isa_dark_green}e1} = {\color{isa_dark_green}e}\env{visited := visited e $\cup$ \{{\color{isa_dark_green}v}\}, stack := ({\color{isa_dark_green}v} \# stack {\color{isa_dark_green}e})};\\
    $~~~~~~~~~~${\color{isa_dark_green}e'} = {\color{isa_dark_blue}dfss} {\color{isa_dark_green}v} (successors {\color{isa_dark_green}v}) {\color{isa_dark_green}e1}\\
    $~~~~~${\color{isa_blue}{in if}} {\color{isa_dark_green}v} = hd(stack {\color{isa_dark_green}e'})\\
    $~~~~~~~~~~${\color{isa_blue}{then}} {\color{isa_dark_green}e'}\env{sccs:=sccs {\color{isa_dark_green}e'} $\cup$ {$\mathcal{S}$ {\color{isa_dark_green}e' v}}, explored:=explored {\color{isa_dark_green}e'} $\cup$ ($\mathcal{S}$ {\color{isa_dark_green}e' v}), stack:=tl(stack {\color{isa_dark_green}e'})}\\
    $~~~~~~~~~~${\color{isa_blue}else} {\color{isa_dark_green}e'})"\\
    | "{\color{isa_dark_blue}dfss} {\color{isa_dark_green}v vs e} =\\
    $~~~~~$({\color{isa_blue}if} {\color{isa_dark_green}vs} = \{\} {\color{isa_blue}then} {\color{isa_dark_green}e}\\
    $~~~~~${\color{isa_blue}else} ({\color{isa_blue}let} {\color{isa_dark_green}w} = SOME {\color{isa_dark_green}x}. {\color{isa_dark_green}x} $\in$ {\color{isa_dark_green}vs}\\
    $~~~~~~~~~~${\color{isa_blue}in} ({\color{isa_blue}let} {\color{isa_dark_green}e'} = ({\color{isa_blue}if} {\color{isa_dark_green}w} $\in$ explored {\color{isa_dark_green}e} {\color{isa_blue}then} {\color{isa_dark_green}e}\\
    $~~~~~~~~~~~~~~~~~~~${\color{isa_blue}else if} {\color{isa_dark_green}w} $\notin$ visited {\color{isa_dark_green}e} {\color{isa_blue}then} {\color{isa_dark_blue}dfs} {\color{isa_dark_green}w e}\\
    $~~~~~~~~~~~~~~~~~~~${\color{isa_blue}else} unite {\color{isa_dark_green}v w e})\\
    $~~~~~~~~~~~~~~${\color{isa_blue}in} {\color{isa_dark_blue}dfss} {\color{isa_dark_green}v} ({\color{isa_dark_green}v} - \{{\color{isa_dark_green}w}\}) {\color{isa_dark_green}e'})))"\\
    $~~~${\color{isa_blue}by} pat\_completeness (force\bblue{+})\\
}

>>>>

\isabelle{
    {\color{isa_blue}{function}} dfs :: "\generic{v} $\Rightarrow$ \generic{v} env $\Rightarrow$ \generic{v} env" \and{}\\
    $~~~~~~~~~~$dfss:: "\generic{v} $\Rightarrow$ \generic{v} set $\Rightarrow$ \generic{v} env $\Rightarrow$ \generic{v} env" \where\\
    "{\color{isa_dark_blue}dfs} {\color{isa_dark_green}v e} =\\
    $~~~~~$({\color{isa_blue}{let}} {\color{isa_dark_green}e1} = {\color{isa_dark_green}e}\env{visited := visited e $\cup$ \{{\color{isa_dark_green}v}\}, stack := ({\color{isa_dark_green}v} \# stack {\color{isa_dark_green}e})};\\
    $~~~~~~~~~~${\color{isa_dark_green}e'} = {\color{isa_dark_blue}dfss} {\color{isa_dark_green}v} (successors {\color{isa_dark_green}v}) {\color{isa_dark_green}e1}\\
    $~~~~~${\color{isa_blue}{in if}} {\color{isa_dark_green}v} = hd(stack {\color{isa_dark_green}e'})\\
    $~~~~~~~~~~${\color{isa_blue}{then}} {\color{isa_dark_green}e'}\env{sccs:=sccs {\color{isa_dark_green}e'} $\cup$ \{$\mathcal{S}$ {\color{isa_dark_green}e' v}\}, explored:=explored {\color{isa_dark_green}e'} $\cup$ ($\mathcal{S}$ {\color{isa_dark_green}e' v}), stack:=tl(stack {\color{isa_dark_green}e'})}\\
    $~~~~~~~~~~${\color{isa_blue}else} {\color{isa_dark_green}e'})"\\
    | "{\color{isa_dark_blue}dfss} {\color{isa_dark_green}v vs e} =\\
    $~~~~~$({\color{isa_blue}if} {\color{isa_dark_green}vs} = \{\} {\color{isa_blue}then} {\color{isa_dark_green}e}\\
    $~~~~~${\color{isa_blue}else} ({\color{isa_blue}let} {\color{isa_dark_green}w} = SOME {\color{isa_dark_green}x}. {\color{isa_dark_green}x} $\in$ {\color{isa_dark_green}vs}\\
    $~~~~~~~~~~${\color{isa_blue}in} ({\color{isa_blue}let} {\color{isa_dark_green}e'} = ({\color{isa_blue}if} {\color{isa_dark_green}w} $\in$ explored {\color{isa_dark_green}e} {\color{isa_blue}then} {\color{isa_dark_green}e}\\
    $~~~~~~~~~~~~~~~~~~~${\color{isa_blue}else if} {\color{isa_dark_green}w} $\notin$ visited {\color{isa_dark_green}e} {\color{isa_blue}then} {\color{isa_dark_blue}dfs} {\color{isa_dark_green}w e}\\
    $~~~~~~~~~~~~~~~~~~~${\color{isa_blue}else} unite {\color{isa_dark_green}v w e})\\
    $~~~~~~~~~~~~~~${\color{isa_blue}in} {\color{isa_dark_blue}dfss} {\color{isa_dark_green}v} ({\color{isa_dark_green}v} - \{{\color{isa_dark_green}w}\}) {\color{isa_dark_green}e'})))"\\
    $~~~${\color{isa_blue}by} pat\_completeness (force\bblue{+})\\
}
